\LARGE \bf When Children Teach a Robot to Write: An Autonomous Teachable Humanoid Which Uses Simulated Handwriting

### 2014-12-12 main.tex
Rephrase the related work section

\section{Related work}
Teachable computer-based agents have previously been used to encourage the 
``protégé effect'', wherein students invest more effort into learning when it
is for a teachable agent than for themselves~\cite{Chase2009}. As we are 
concerned with learning of a physical skill, the learning agent developed is 
embodied in a humanoid robot which is capable of physically demonstrating 
handwriting trajectories to its child learning partner.
This is supported by the potential for motor mimicry to yield significant 
improvements in handwriting interventions in which letter formations are 
demonstrated to participants~\cite{Berninger1997}. Furthermore, when compared
to screen-based agents, robotic partners have been shown in some contexts to 
increase users' compliance with tasks~\cite{Bainbridge2011}, maintain more 
effective long-term relationships~\cite{Kidd2008}, and produce greater 
learning gains when acting as tutors~\cite{Leyzberg2012}: benefits which we
hope will transfer into this application.

Robots have been used as teachers or social partners to promote children's
learning in a range of contexts, most commonly langauge skills~\cite{Han2010}, 
but also applications such as logic puzzles~\cite{Leyzberg2014}, in music 
classes~\cite{Han2009}, and physical skills such as caligraphy \cite{Matsui2013}.
Werfel suggests in~\cite{Werfel2014} that, until now, most of the work 
investigating how humans can instead teach robots (language \cite{Saunders2010} or 
table tennis \cite{Mulling2013}, for example) focuses on the robot's
benefits rather than the learning experienced by the human tutor. Our
work concentrates on this latter aspect. We note that our work differs from those
where a robot develops physical skills through `learning 
from demonstration' from humans, as the agent we present is only simulating 
fine motor skills for interaction purposes.

A robotic learning agent which 
employs the learning by teaching paradigm has 
previously been developed by Tanaka and Matsuzoe~\cite{Tanaka2012}. In their
system, children learn vocabulary by teaching the {\sc nao} robot to act out 
verbs. The robot is tele-operated and mimics the actions that the children
teach it, but with no long-term memory or learning algorithm in place.
Our project significantly extends this line of work in two ways. First, by
proposing a robotic partner which is fully autonomous in its learning,
and second, by investigating the context
of children's acquisition of a challenging physical skill (handwriting).

>>>>

\section{Related work}

Teachable computer-based agents have previously been used to encourage the
``protégé effect'', wherein students invest more effort into learning when it is
for a teachable agent than for themselves~\cite{Chase2009}.  As we are concerned
with learning of a physical skill, the learning agent developed is embodied in a
humanoid robot which is capable of physically demonstrating handwriting
trajectories to its child learning partner.  This is supported by the potential
for motor mimicry to yield significant improvements in handwriting interventions
in which letter formations are demonstrated to
participants~\cite{Berninger1997}. Furthermore, when compared to screen-based
agents, robotic partners have been shown in some contexts to increase users'
compliance with tasks~\cite{Bainbridge2011}, maintain more effective long-term
relationships~\cite{Kidd2008}, and produce greater learning gains when acting as
tutors~\cite{Leyzberg2012} that can be adapted to each
learner~\cite{Leyzberg2014}.

Robots have been used as teachers or social partners to promote children's
learning in a range of contexts, most commonly related to language
skills~\cite{Han2010}, and less often to physical skills (such as
calligraphy~\cite{Matsui2013}).  Looking at the converse (humans \emph{teaching}
robots), Werfel notes in~\cite{Werfel2014} that most of the work focuses on the
robot's benefits (in terms of language~\cite{Saunders2010} or
physical~\cite{Mulling2013} skills, for example) rather than the learning
experienced by the human tutor itself.  Our work concentrates on this latter
aspect: by demonstrating handwriting to a robot, we aim at improving the
\emph{child} performances. Note that our work must be distinguished from
traditional ``learning from demonstration'' approaches, as the agent we present
is only simulating fine motor skills for interaction purposes.

A robotic learning agent which employs the learning by teaching paradigm has
previously been developed by Tanaka and Matsuzoe~\cite{Tanaka2012}. In their
system, children learn vocabulary by teaching the {\sc nao} robot to act out
verbs. The robot is tele-operated and mimics the actions that the children teach
it, but with no long-term memory or learning algorithm in place.  Our project
significantly extends this line of work in two ways. First, by investigating the
context of children's acquisition of a challenging physical skill (handwriting),
and second by proposing a robotic partner which is fully autonomous in its
learning.
